---
title: "multiple_possibilities_GLMM"
author: "Christoph Voelter"
date: "November 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")

```

## Data import

Preparing code for mixed modeling. 

```{r loading data, include = FALSE}

all.data <- read.table(file="Data_multiple future possibilities_Oct2018.txt", header=T, sep="\t")

```



## Mixed modeling with all relevant varaibles predicting accuracy

``` {r mixed modeling, error=TRUE}

# centering variables for modeling

model.data <- all.data %>%
  mutate(z.trial = scale(trial, scale = T, center = T),
         condition = relevel(condition, ref = "control"))


## code to run the model
mm.1 <- glmer(both_ropes ~ condition + z.trial + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
             #, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

## CIs
#confint(mm.1, method='profile')
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=F)
#round(boot.res,3)

## save model output
saveRDS(mm.1, "multpos_model.rds")
```

####Null model	 
```{r}	 
mm.1.null <- glmer(both_ropes ~ 1 + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
            # , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm.1, mm.1.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.1, test="Chisq")
round(xdrop1,3)
```


## check for colinearity in the previous model.

```{R}
library (car)

col.mm1 <- glm(both_ropes ~ condition + z.trial 
             , data = model.data
             , family = binomial
)
vif(col.mm1)
#no problem
```


`````` {r plot mixed modeling, error=TRUE}

### Model plotting

plot_model(mm.1, type='est') 
plot_model(mm.1, type='re') 
## sjp.lmer will be deprecated eventually, and plot_model can be used to precisely obtain which plots of the GLMM one wishes to examine.
sjp.lmer(mm.1)



```





