---
title: "multiple_possibilities_GLMM"
author: "Christoph Voelter"
date: "April 04, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library (car)
library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
library(ggplot2)
library(scales)
source("../../R scripts/Roger/diagnostic_fcns.r")
source("../../R scripts/Roger/glmm_stability.r")
source("../../R scripts/Roger/boxplotteR.r")
source("../../R scripts/Roger/boot_glmm.r")
source("../../R scripts/Roger/corr_exact.r")
#load(file ="mm1_mult_poss.RData")
#readRDS(file ="multpos_model.rds")
```

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="Data_multiple future possibilities_Apr2019.txt", header=T, sep="\t")
str(all.data)

```

```{r eval=FALSE}

capFirst <- function(s) {
    paste(toupper(substring(s, 1, 1)), substring(s, 2), sep = "")
}

all.data$chimp <- capFirst(all.data$chimp)
str(all.data)
```


##Summary
Both the paired-samples t-test and a mixed model show a significant effect for condition. There was no significant interaction between session and condition. 


##Plotting data
```{r error=FALSE, echo=FALSE}

plot_individual <- all.data %>%
  group_by(condition, chimp) %>% 
  summarize(correct_resp = sum(both_ropes)) 

plot_ind2 <- plot_individual %>% add_count(correct_resp)
ggplot(
  data=plot_ind2, aes(condition, correct_resp, group = chimp)) +   
  geom_point(size = plot_ind2$n, colour = "purple") +
  geom_line(lty=2)+
  #ylim(0,12)+
  labs(x="Condition",y="Sum of both ropes pulled")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,12,2))


```



```{r error=FALSE, echo=FALSE}

theme_set(theme_classic())

# Plot
ggplot(all.data, aes(x=factor(chimp), y=factor(trial_total), group=pull_action)) + 
  geom_point(stat='identity', aes(shape=pull_action, col=correct), size=5) +
  scale_shape_manual(values=c(7,15), name="Ropes pulled")+
      scale_color_manual(name="Reward obtained", 
                     labels = c("no", "yes"), 
                     values = c("yes"="#00ba38", "no"="darkblue")) +
# 
#   geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(trial), 
#                    yend=max(trial)), 
#              #  linetype="dashed", 
#                size=0.5,
#                colour="grey") +
#     geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(7), 
#                    yend=max(18)), 
#              #  linetype="dashed", 
#                size=0.5,
#                colour="grey") +
#      geom_segment(aes(x=chimp, 
#                    xend=chimp, 
#                    y=min(19), 
#                    yend=max(24)), 
#               # linetype="dashed", 
#                size=0.5,
#                colour="grey") + 
 theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  axis.ticks = element_blank())+
  geom_hline(yintercept=6.5, linetype="dashed", "black", size=0.75)+
  geom_hline(yintercept=18.5, linetype="dashed", "black", size=0.75)+
 # scale_x_discrete(name ="Chimp ID")+
  scale_y_discrete(breaks=c(3,12,22),labels=c("Transparent 1", "Opaque", "Transparent 2"))+ #name= "Condition",
  guides(color = guide_legend(order = 2),
         shape = guide_legend(order = 1))+
  coord_flip()

ggsave("multiple possibilities_plot.tiff", width = 18, height = 10, units = "cm")

```





\pagebreak  

##Paired-sample t-test
```{r}

contr_data <- plot_individual %>%  
  filter(condition == "control")

exp_data <- plot_individual %>%  
  filter(condition == "test")


t.test(exp_data$correct_resp, contr_data$correct_resp, paired = TRUE, alternative = "two.sided")
```

## GLMM

###GLMM 01 with session * condition interaction

``` {r mixed modeling, error=TRUE}

# centering variables for modeling
model.data <- all.data %>% 
  mutate(z.trial = scale(trial, scale = T, center = T),
         z.session = scale(session, scale=T, center=T),
         condition = relevel(condition, ref = "control"))

## code to run the model
mm.1 <- glmer(both_ropes ~ condition*z.session + z.trial + 
               (1+ z.session*condition+z.trial|chimp)
             , data = model.data
             , family = binomial
            , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```

```{r include=FALSE}
## save model output
#saveRDS(mm.1, "multpos_model.rds")
#save.image("mm1_mult_poss.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res, "multpos_model.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model.rds"), 3)
```

####Null model	 
```{r}	 
mm.1.null <- glmer(both_ropes ~ 1 + 
                (1+ z.session*condition+z.trial|chimp)
             , data = model.data
             , family = binomial
            , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm.1, mm.1.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.1, test="Chisq")
round(xdrop1,3)
```

###GLMM02 without the interaction


``` {r mixed modeling2, error=TRUE}

mm.2 <- glmer(both_ropes ~ condition+z.session + z.trial + 
               (1+ z.session+condition+z.trial|chimp)
             , data = model.data
             , family = binomial
            , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)
```



``` {r include=FALSE}
## save model output
#saveRDS(mm.2, "multpos_model.rds")
#save.image("mm2_mult_poss.RData")
```

####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R eval=FALSE}		
boot.res2=boot.glmm(model.res=mm.2, excl.warnings=T,nboots=1000, para=T)
saveRDS(boot.res2, "multpos_model2.rds")
```

```{R echo=FALSE}		
round(readRDS(file ="multpos_model2.rds"), 3)
```

####Null model	 
```{r}	 
mm.2.null <- glmer(both_ropes ~ 1 + 
               (1+ z.session+condition+z.trial|chimp)
             , data = model.data
             , family = binomial
            , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm.2, mm.2.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.2)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.2, test="Chisq")
round(xdrop1,3)
```




#### check for colinearity in the previous model.

```{R echo=FALSE, error=FALSE, warning=FALSE}

col.mm1 <- glm(both_ropes ~ condition + z.trial +z.session
             , data = model.data
             , family = binomial
)
vif(col.mm1)
#no problem
```
-> no collinearity

####Model output
`````` {r plot mixed modeling, error=TRUE, warning=FALSE}

plot_model(mm.2, type='est') 
plot_model(mm.2, type='re') 
```





