---
title: "multiple_possibilities_GLMM"
author: "Christoph Voelter"
date: "November 1, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(lme4)
library(readr)
library(tidyverse)
library(sjPlot)
library(ggthemes)
source("C:/Users/cjv3/R/R scripts/Roger/diagnostic_fcns.r")
source("C:/Users/cjv3/R/R scripts/Roger/glmm_stability.r")
source("C:/Users/cjv3/R/R scripts/Roger/boxplotteR.r")
source("C:/Users/cjv3/R/R scripts/Roger/boot_glmm.r")
source("C:/Users/cjv3/R/R scripts/Roger/corr_exact.r")
load("mm1_mult_poss.RData")

```

```{r loading data, include = FALSE}
#Preparing code for mixed modeling. 
all.data <- read.table(file="Data_multiple future possibilities_Oct2018.txt", header=T, sep="\t")

```

##Plotting data
```{r error=FALSE}

plot_individual <- all.data %>%
  group_by(condition, chimp) %>% 
  summarize(correct_resp = sum(both_ropes)) 

plot_ind2 <- plot_individual %>% add_count(correct_resp)
ggplot(
  data=plot_ind2, aes(condition, correct_resp, group = chimp)) +   
  geom_point(size = plot_ind2$n, colour = "purple") +
  geom_line(lty=2)+
  #ylim(0,12)+
  labs(x="Condition",y="Sum of both ropes pulled")+
  theme_few()+
  scale_y_continuous(breaks=seq(0,12,2))


```


###Summary
Both the paired-samples t-test and a mixed model show a significant effect for condition. Obviously, there is a lot of uncertainty regarding the strength of the effect of condition given the small sample size.


##Paired-sample t-test
```{r}

contr_data <- plot_individual %>%  
  filter(condition == "control")

exp_data <- plot_individual %>%  
  filter(condition == "test")


t.test(exp_data$correct_resp, contr_data$correct_resp, paired = TRUE, alternative = "two.sided")
```

## GLMM

``` {r mixed modeling, error=TRUE}

# centering variables for modeling
model.data <- all.data %>% 
  mutate(z.trial = scale(trial, scale = T, center = T),
         condition = relevel(condition, ref = "control"))

## code to run the model
mm.1 <- glmer(both_ropes ~ condition + z.trial + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
             #, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

## save model output
#saveRDS(mm.1, "multpos_model.rds")
#save.image("mm1_mult_poss.RData")
```
####Confidence intervals
Confidence intervals for the binomial models were derived using the function bootMer of the R package lme4, using 1,000 parametric bootstraps and bootstrapping over the random effects.

```{R}		
#boot.res=boot.glmm(model.res=mm.1, excl.warnings=T,nboots=1000, para=F)
#saveRDS(mm.1, "multpos_model.rds")
round(boot.res,3)
```

####Null model	 
```{r}	 
mm.1.null <- glmer(both_ropes ~ 1 + 
               (1 + condition + z.trial |chimp)
             , data = model.data
             , family = binomial
            # , control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5))
)

```
####Full-null model comparison
```{r}	 
anova(mm.1, mm.1.null, test="Chisq")
```
####Model output
  + Coefficients
```{r}
round(summary(mm.1)$coefficients, 3)
```
  + Individual predictors: likelihood ratio tests  
Drop1: P values for the individual effects were based on likelihood ratio tests comparing the full with respective reduced models (Barr et al., 2013; R function drop1 with argument 'test' set to "Chisq"). 
```{r}
xdrop1=drop1(mm.1, test="Chisq")
round(xdrop1,3)
```


## check for colinearity in the previous model.

```{R include=FALSE}
library (car)

col.mm1 <- glm(both_ropes ~ condition + z.trial 
             , data = model.data
             , family = binomial
)
vif(col.mm1)
#no problem
```
-> no collinearity

`````` {r plot mixed modeling, error=TRUE}

### Model plotting

plot_model(mm.1, type='est') 
plot_model(mm.1, type='re') 




```





